---
title: "bingmapr-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bingmapr-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bingmapr)
```

`bingmapr` is a wrapper for the Bing Maps API written in R. It currently includes wrapper functions for several of the Locations API functions, including geocoding, reverse geocoding, and location recognition, as well as a function for batch geocoding from a CSV.

In order to make use of any of the functions contained within this package, you must first obtain a Bing Maps API key [here](https://www.bingmapsportal.com). Once you have your key, you must set it as an environment variable with name `api_key`:

```{r, eval=FALSE}
Sys.setenv(api_key='your_key_here')
```

Doing this will store your API key for your entire R session, allowing you to make multiple calls using the various wrapper functions within `bingmapr` without having to specify your API key each time.

## Geocode

The `geocode` function can be used to geocode an address using the Bing Maps Locations API. It takes any combination of addressLine, locality, adminDistrict, postalCode, and countryRegion, and returns a geocoded coordinate pair corresponding to that location as well as other information about the location. If you are geocoding an address in the USA, you can think of these parameters as representing street address, city, state, ZIP code, and country abbreviation (US), respectively.

For example, suppose we wished to obtain the coordinates for Apple Park, located at One Apple Park Way in Cupertino, CA (zipcode 95014). We can use the `geocode` function to accomplish this:

```{r}
applepark_geocode <- geocode(addressLine='One Apple Park Way',locality='Cupertino',adminDistrict='CA',postalCode='95014',countryRegion='US')
```

We can then print the response of our geocode request:

```{r}
print(applepark_geocode)
```

Let's take a closer look at the object returned by `geocode`.

```{r}
print(typeof(applepark_geocode))
print(names(applepark_geocode))
```

We see that `geocode` returns a named list with four parts: "chords", "content", "params", and "response". We can examine these individually:


**chords**: A named list containing the geocoded latitude and longitude coordinates for the location
```{r}
print(applepark_geocode['chords'])
```

**content**: A named list containing the complete response returned from the API. This includes not only the geocoded coordinates, but also information such as the confidence score of the geocode, the entity type of the returned coordinates, and aspects of the address that were not inputted as arguments into the API (here, for example, we are told that Apple Park is located in Santa Clara County, which we did not specify in our call to `geocode`).
```{r}
print(applepark_geocode['content'])
```

**params:** A named list containing the location parameters given as input to the `geocode` function.
```{r}
print(applepark_geocode['params'])
```

**response:** The response returned from the `httr` library. This includes information about the request and the response returned from the API, including the URL and the date/time of the request, as well as the status code, encoding type, and file size of the response.
```{r}
print(applepark_geocode['response'])
```

## reverse_geocode

The `reverse_geocode` function can be used to reverse geocode an address using the Bing Maps Locations API. It essentially performs the opposite task of the `geocode` function, in that it takes in a latitude and longitude pair and returns the addressLine, locality, adminDistrict, postalCode, and countryRegion corresponding to the address at that location.

Continuing with our Apple Park example from the `geocode` function, suppose we had the coordinate pair (37.3348,-122.0091), and wished to obtain the address associated with this location. We can accomplish this using `reverse_geocode`:

```{r}
applepark_reverse_geocode <- reverse_geocode(lat=37.3348,long=-122.0091)
```

We can print the response of our reverse geocode call:

```{r}
print(applepark_reverse_geocode)
```

Once again, we can examine the structure of the returned object:

```{r}
print(typeof(applepark_reverse_geocode))
print(names(applepark_reverse_geocode))
```

Here, we see that the structure of the object is very similar to that of the `geocode` function, with the only difference being the inclusion of "address" instead of "chords" since we are now reverse geocoding. Given the high degree of similarity in output between `geocode` and `reverse_geocode`, I will not go into detail in explaining the output here. Please see the above example of `geocode` for a more detailed explanation.

**address:** Contains the complete geocoded address.
```{r}
print(applepark_reverse_geocode['address'])
```

**content:** Contains similar information about the location as was returned in `geocode`.
```{r}
print(applepark_reverse_geocode['content'])
```

## location_recognition

The `location_recognition` function can be used to find a list of entities, including both businesses and natural points of interest, located within a given radius of an inputted coordinate pair using the Bing Maps Location API. It takes a latitude and longitude pair, radius size, and top parameter indicating the number of nearby locations to return as input as its key input parameters, and returns a list of nearby entities (separated between "business" and "natural POI") with information including their name, address, and contact information.

For example, suppose we wished to find a list of 3 entities within a 0.5 mile radius of the coordinate pair (37.7734,-122.4216), a location in San Francisco. We will specify the radius parameter as 0.5 so that the API to limit its search radius to locations within 0.5 miles of our inputted coordinate pair (kilometers can be used by setting the "distanceUnit" parameter equal to "km"). We will set the top parameter equal to 3, causing the API to return a maximum of 3 nearby locations (if the number of entities found within your specified search radius is less than your top parameter, then the number of entities returned will be less).

We are ready to make our call to `location_recognition`:
```{r}
sf_lr <- location_recognition(lat=37.7734,long=-122.4216,radius=0.5,top=3)
```

We can print the object returned by the function:
```{r}
print(sf_lr)
```

Let's take a closer look at the structure of the object returned by `location_recognition`:

```{r}
print(typeof(sf_lr))
print(names(sf_lr))
```

We see here that `location_recognition` returns a named list with four parts: "business", "naturalPOI", "params", and "response". The "params" and "response" sections include the same information as in the `geocode` and `reverse_geocode` functions, so I will not cover them here (please see the above example of `geocode` for an explanation of these sections).

The locations returned by `location_recognition` are separated by entity type under the "business" and "naturalPOI" sections of the response object. We can examine each of these for our example:

**business:**
```{r}
print(sf_lr$business)
```
We see here that the Location Recognition API found 3 business locations within 0.5 miles of (37.7734,-122.4216). The names of these entities are "Edwardian Hotel", a business of type "Hotels"; "Sow Juice Pop-up", a business of type "Fast Food"; and "Zuni Café", a business of type "French Restaurant". We are given a variety of information about the detailed type of each business, as well as its website, phone number, address, and coordinates.

Given that all 3 of our requested entities happened to be of type "business", we would not expect any natural POIs to have been returned. We can confirm this by examining the corresponding section of the returned object:
```{r}
print(sf_lr$naturalPOI)
```
We are given an empty list, indicating that no natural POIs were returned.

## geocode_csv

The `geocode_csv` function is designed to perform bulk geocoding of addresses from a CSV file using the `geocode` function of `bingmapr`. It takes a path to a CSV as well as strings representing the column names that correspond to each part of the address to geocode as inputs, and returns a tibble containing the original CSV with the columns "latitude" and "longitude" appended. It also write a copy of this tibble to disk as a CSV in the same location as the original CSV, with `_geocoded` appended to the filename.

For example, suppose we had a CSV file located in the path `/users/ericphillips/Downloads/sf_starbucks.csv` containing addresses corresponding to the company owned Starbucks locations in San Francisco that we wished to geocode. In this file, the column "street_address" corresponds to the addressLine, "city" corresponds to the locality, "state" corresponds to the adminDistrict, "zipcode" corresponds to the postalCode, and "country" corresponds to the countryRegion (please see the `geocode` example above for more information about these location classifications).

We can execute this operation using `geocode_csv` (this operation is not executed when the vignette is built due to the large number of API requests that it entails):
```{r,eval=FALSE}
sf_starbucks_geocoded <- geocode_csv('/users/ericphillips/Downloads/sf_starbucks.csv',addressLine_col='street_address',locality_col='city',adminDistrict_col='state',postalCode_col='zipcode',countryRegion_col='country')
```

We can examine the first few rows of the tibble returned by `geocode_csv`:
```{r,eval=FALSE}
head(sf_starbucks_geocoded,6)
```
The columns "latitude" and "longitude" correspond to the geocoded coordinates returned from the `geocode` function (the columns "lat" and "long" were part of the original dataset). A quick scan reveals that the geocoded coordinates seem to match up closely with the original coordinates, suggesting that our results are accurate.
